Theoretical prediction of disrupted Min oscillation in flattened \emph{Escherichia coli}

### 2015-03-31 paper/plos.tex
changed one citation and one line in bib Tested everything on crystal.

Both Fig.~\ref{image-p} and its associated movies (see supplementary
material), show that the stochastic model exhibits a ``starry night''
effect characterized by spatially fixed points of protein density
build up, as recruitment leads to clusters of MinD forming on the wall
and then subsequently dissipating.  This results from the omission of
diffusion along the membrane from Huang's model, which would allow
these recruitment clusters to spread out.  Experiments have confirmed
that diffusion along the membrane does occur, albeit with a rate two
orders of magnitude lower than that in the
cytoplasm~\cite{meacci2005min}.  The `stars' in the effect typically
last for around 10 seconds. The membrane-bound proteins will diffuse
by a distance of around one micron during this time, which is enough
to spread out across the polar section of the one micron diameter
wild-type pill cells.  As we see below, the flattened, irregular cells
are large enough that this one micron blurring would not completely
eliminate this `starry night' effect.

>>>>

Both Fig.~\ref{image-p} and its associated movies (see supplementary
material), show that the stochastic model exhibits a ``starry night''
effect characterized by spatially fixed points of protein density
build up, as recruitment leads to clusters of MinD forming on the wall
and then subsequently dissipating.  This results from the omission of
diffusion along the membrane from Huang's model, which would allow
these recruitment clusters to spread out.  Experiments have confirmed
that diffusion along the membrane does occur, albeit with a rate two
orders of magnitude lower than that in the
cytoplasm~\cite{meacci2006mobility}.  The `stars' in the effect typically
last for around 10 seconds. The membrane-bound proteins will diffuse
by a distance of around one micron during this time, which is enough
to spread out across the polar section of the one micron diameter
wild-type pill cells.  As we see below, the flattened, irregular cells
are large enough that this one micron blurring would not completely
eliminate this `starry night' effect.
